Implementing Real-time Transport Services over an Ossified Network

### 2016-05-10 paper.tex
Update re Marwan's comment

we also assert that these services can be deployed over TCP. How? TCP
Hollywood offers a prototype. 
brief summary.
obviously we need to change TCP congestion control too.

>>>>

these services are deployed over TCP now, but have an inconvenient API that
imposes lots of work on application developers, and with higher than desired
latency. 
TCP Hollywood offers a way to fix both issues.
Brief summary.
Obviously we need to change TCP congestion control too.
